Comparing efficiency of R packages implementing calculation of persistent homology

### 2019-10-27 tdabench-paper/tdabench-paper.Rmd
Added tentative figure descriptions

There will likely be several sections, perhaps including code snippets, such as:

```{r}
x <- 1:10
x
```

>>>>

Figure 1: Comparison of persistent homology calculation runtimes across R packages for a torus. Panel 2. Horizontal axis: number of points in torus. Vertical axis: runtime. Point chart. Point color: underlying engine. Point shape: same as color. Panel 1. Torus showing users visual representation of dataset/point cloud. Goal: overview showing speed differences across engines on a canonical shape.

Figure 2: Comparison of persistent homology calculation runtimes across R packages for n-dimensional boxes (n = 2, 3, 4, 5). For each dimension, features up to n-1 dimensions are calculated. Panel 1. Visual representation of 2-d box (maybe points, maybe box, maybe scattered both). Panel 2. Visual representation of 3-d box (maybe points, maybe box, maybe both scattered). Panels 3-6 (differing n={2,3,4,5} for dimension). Point shape/color: underlying engine. Horizontal axis: number of points. Vertical axis: runtime.

Figure 3: Runtime of persistent homology calculation as a function of underlying engine (4d noisy circle/annulus). Panel 1: visualize noisy circle - use imagination for 4d. Panel 2. Horizontal axis: number of points. Vertical axis: runtime. Point color/shape: underlying engine. Goal: show that TDAstats and GUDHIalpha are sufficiently faster than GUDHI and Dionysus, so the latter pair can be ignored for rest of figures.

Figure 4: Runtime of persistent homology calculation as a function of underlying engine and feature dimension (4d noisy circle/annulus). Panel 1 = GUDHI alpha engine. Horizontal axis = number of points. Vertical axis = runtime. Point color/shape = feature dimension. Panel 2 = panel 1, but with TDAstats engine. Goal: show how increasing dimension slows down the calculation time.

Figure 5: Memory use of Rips complex vs alpha complex. Engine = GUDHI(alpha). Panel 1 = 4-sphere. Panel 2 = 3-annulus. Panel 3 = torus. Panel 4 = 5-box. For each panel: point color/shape = engine (GUDHI vs alpha); horizontal axis = number of points; vertical axis = memory use; feature dimension = data dimension - 1 for all panels. Goal: compare memory
POINT OUT THAT RIPSER DOESN'T MEASURE MEMORY B/C NO BOUNDARY MATRIX, BUT LIKELY SOMEWHERE IN BETWEEN THE TWO

Figure 6: Same as Figure 5, but TDAstats vs GUDHIalpha for runtime.
